### 2014-06-05 writing/S'14 paper/join.tex
Adding first two batches of new results.

\paragraph{Results.} We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier, though the performance of the model was
not highly sensitive to either dimensionality parameter in any of the experiments discussed here. This
model was able to correctly label 99.3\% of the provably derivable test
examples, and 99.1\% of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 90.0\% and 87.0\%, respectively.

@@

% TODO: T-sne the RNTN model's embeddings.

>>>>

\paragraph{Results.} We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier, though the performance of the model was
not highly sensitive to either dimensionality parameter in any of the experiments discussed here. This
model was able to correctly label 99.4\% (94.3 macroaveraged F1) of the provably derivable test
examples, and 95.4\% (92.2) of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 89.0\% (80.9)  and 62.5\% (40.1), respectively. Training accuracy was 99.8\% for the RNTN and 95.4\% for the RNN.

@@

### 2014-06-05 writing/S'14 paper/recursion.tex
Adding first two batches of new results.

\paragraph{Results.} We trained both the RNN and RNTN models on the data of size four or
less (65k pairs), and tested it on examples of up to size 12 (44k
pairs). We initialized the model parameters randomly, including the
vector representations of the six variables. The results are shown in
Figure~\ref{prop-results}. In tuning, we found that the RNN model was
approximately optimal with 45-dimensional vector representations, and
the RNTN model was approximately optimal with 25 dimensions. We fixed
the size of the feature vector for the classifier at 75 dimensions. We
found that the RNTN model was able to perform almost perfectly on
unseen small test examples, with accuracy above 99\% below size four.
After depth four, performance gradually falls with increasing size.
The RNN model did not perform well, reaching only 88.2\% accuracy on
the smallest test examples, and declining from there to near-baseline
performance at size 12.

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_results\string_updated.eps}
  \caption{Model performance on propositional logic, by expression size. The dashed line indicates that only expressions of size four or less appeared in the training data.}  
  \label{prop-results}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.5in]{recursion\string_pairwise.eps}
  \caption{How well each model can distinguish to expressions that differ by one term, measured for terms embedded under different numbers of tokens of \ii{and}.}  
  \label{prop-falloff}
\end{figure}

>>>>

\paragraph{Results.} We trained both the RNN and RNTN models on the data of size four or
less (65k pairs), and tested it on examples of up to size 12 (44k
pairs). We initialized the model parameters randomly, including the
vector representations of the six variables. The results are shown in
Figure~\ref{prop-results}. In tuning, we found that the RNN model was
approximately optimal with 45-dimensional vector representations, and
the RNTN model was approximately optimal with 25 dimensions. We fixed
the size of the feature vector for the classifier at 75 dimensions. We
found that the RNTN model was able to perform almost perfectly on
unseen small test examples, with accuracy above 99\% below size four (Macroaveraged F1 was above 98.9).
Starting at size four, performance gradually falls with increasing size.
The RNN model did not perform well, reaching only 88.2\% (67.2) accuracy on
the smallest test examples, and declining from there to near-baseline
performance at size 12. Training accuracy was 99.6\% for the RNTN and 87.6\% for the RNN.

% thu-and-or-deep-25-32b.txt iter 102
% mon-and-or-deep-45r-32.txt iter 480

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.3in]{recursion\string_results\string_updated.eps}
  \caption{Model performance on propositional logic, by expression size. The dashed line indicates that only expressions of size four or less appeared in the training data.}  
  \label{prop-results}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=5.3in]{recursion\string_pairwise.eps}
  \caption{How well each model can distinguish to expressions that differ by one term, measured for terms embedded under different numbers of tokens of \ii{and}.}  
  \label{prop-falloff}
\end{figure}
